Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-08-25 draftfinalreport_v4.Rnw
remove TODOs
update cost benefit table to reduce fontsize, fix NPV col

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TABLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% double check what the intercept is (age0-2:euro:nzdep1-3?) w JM %%%%%%%%%%%%%
%%%%%%%%%%%%%% add to the caption text %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE TEXT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% NIGEL DISLIKES ALL THE HYPERLINKS - CHANGE TO 'Figures 26--37' ? %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE/BELOW RE REGRESSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% NF COMMENT - WHAT'S THE AIM OF THE REGRESSION - PARSIMONIOUS MODEL? %%%%%
%%%%%%%%%%%%%%% good point! NOT SURE TC DID AND I LEFT IN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% but %%%%%%%%%%%%% MAYBE IGNORE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%% TODO %%%%%%%%%%%%%%%%%%% ABOVE RE REGRESSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% NF COMMENT - COSTS CALCULATED FROM DATA, SO NOT INDEPENDENT %%%%%%%%%%%%%%
%%%%%%%%%%%%%%% good point! NOT SURE TC DID AND I LEFT IN %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%% but %%%%%%%%%%%%% MAYBE IGNORE AGAIN %%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable20)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV","NPV")
costtable20[,c(2:10,12)] <- round(costtable20[,c(2:10,12)])
costtable20[,11] <- round(costtable20[,11],2)
latex(costtable20, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 20 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio.}
\label{table:cost20}
\end{sidewaystable}

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable50)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable50[,c(2:10,12)] <- round(costtable50[,c(2:10,12)])
costtable50[,11] <- round(costtable50[,11],2)
latex(costtable50, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 50 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost50}
\end{sidewaystable}

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable74)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV","NPV")
costtable74[,c(2:10,12)] <- round(costtable74[,c(2:10,12)])
costtable74[,11] <- round(costtable74[,11],2)
latex(costtable74, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with \$\Sexpr{break_even_vacc_cost} dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost74}
\end{sidewaystable}

@@

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable20_no)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV","NPV")
costtable20_no[,c(2:10,12)] <- round(costtable20_no[,c(2:10,12)])
costtable20_no[,11] <- round(costtable20_no[,11],2)
latex(costtable20_no, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 20 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost20_no}
\end{sidewaystable}

\begin{sidewaystable}\small
<<results=tex,echo=FALSE>>=
colnames(costtable50_no)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable50_no[,c(2:10,12)] <- round(costtable50_no[,c(2:10,12)])
costtable50_no[,11] <- round(costtable50_no[,11],2)
latex(costtable50_no, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 50 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost50_no}
\end{sidewaystable}

>>>>

@@

@@

@@

@@

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable20)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable20[,c(2:10,12)] <- round(costtable20[,c(2:10,12)])
costtable20[,11] <- round(costtable20[,11],2)
latex(costtable20, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 20 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio.}
\label{table:cost20}
\end{sidewaystable}

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable50)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable50[,c(2:10,12)] <- round(costtable50[,c(2:10,12)])
costtable50[,11] <- round(costtable50[,11],2)
latex(costtable50, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 50 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost50}
\end{sidewaystable}

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable74)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable74[,c(2:10,12)] <- round(costtable74[,c(2:10,12)])
costtable74[,11] <- round(costtable74[,11],2)
latex(costtable74, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with \$\Sexpr{break_even_vacc_cost} dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost74}
\end{sidewaystable}

@@

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable20_no)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable20_no[,c(2:10,12)] <- round(costtable20_no[,c(2:10,12)])
costtable20_no[,11] <- round(costtable20_no[,11],2)
latex(costtable20_no, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 20 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}  is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost20_no}
\end{sidewaystable}

\begin{sidewaystable}\footnotesize
<<results=tex,echo=FALSE>>=
colnames(costtable50_no)<-c("DHB", "Vacc", "Vacc costs", "Wages saved", "Manage saved", "Hosp saved", "Contacts","Costs saved", "Outbreak", "OB costs", "B/C","NPV")
costtable50_no[,c(2:10,12)] <- round(costtable50_no[,c(2:10,12)])
costtable50_no[,11] <- round(costtable50_no[,11],2)
latex(costtable50_no, file="", table.env=FALSE,rowname=NULL)
@
\caption{Benefit--cost analyses with 50 dollars per immunised person. \textit{Vacc} is numbers to immunise (see \autoref{table:attack}); \textit{Vacc costs} is cost for the catch up immunisation programme; \textit{Wages saved} is wages of care givers and cases saved (\$839 per case); \textit{Contacts} is costs saved through contact exclusion (\$2,624.57 per case); \textit{Manage saved} is management costs saved (\$1,765 per case), plus \$20 GP costs; \textit{Hosp saved} is the hospitalisation costs saved (\$1,877 per case); \textit{Costs save}  is the discounted costs saved; \textit{Outbreak}	is the predicted median outbreak size despite $R_v < 1$ due to measles importation from 1000 simulations\footnote{Note the median outbreak sizes are what is expected, while the mean takes into account rare, but large outbreaks, see \autoref{fig:sim} and \autoref{fig:sim1}.}; \textit{OB costs}	is costs expected due to continued measles importations based on 10 introductions of measles, one per year, but costs discounted on the same discounted rate; \textit{B/C} is the benefit--cost ratio; \textit{NPV} is the net present value, defined as the sum of the present values of costs and benefits of the vaccination programme. Negative values are costs, positive savings.}
\label{table:cost50_no}
\end{sidewaystable}
